Lines or planes through the origin can be written as spans
of their direction vectors. However, a line or plane that doesn't
pass through the origin cannot be written as a span---it must
be expressed as a \emph{translated} span.

XXX Figure


There's something special about sets that can be expressed as 
(untranslated) spans. In particular, since a linear combination
of linear combinations is still a linear combination, a span
is \emph{closed} with respect to linear combinations. That is, 
by taking linear combinations of vectors in a span, you cannot
escape the span. In general, sets that have this property are called
\emph{subspaces}\index{subspace}.

\SavedDefinitionRender{Subspace}

In the definition of subspace, property (i) is called
	begin \emph{closed with respect to vector addition} and
	property (ii) is called being \emph{closed with respect to
	scalar multiplication}.

Subspaces generalize the idea of \emph{flat spaces through the origin}. They encompass
lines, planes, volumes and more.

\begin{example}
	Let $\mathcal V\subseteq \R^2$ be the complete solution to 
	$x+2y=0$.  Show that $\mathcal V$ is a subspace.

	XXX Finish
\end{example}

\begin{example}
	Let $\mathcal W\subseteq \R^2$ be the line expressed in vector form
	as 
	\[
		\vec x=t\mat{1\\2}+\mat{1\\1}.
	\]
	Determine whether $\mathcal W$ is a subspace.

	XXX Finish
\end{example}


As mentioned earlier, subspaces and spans are deeply connected
by the following theorem.

\begin{theorem}
	Every subspace is a span and every span is a subspace.  More precisely,
	$\mathcal V\subseteq \R^n$ is a subspace if and only if $\mathcal V=
	\Span\mathcal X$ for some set $\mathcal X$.
\end{theorem}
\begin{proof}
	We will start by showing every span is a subspace.  Fix $\mathcal X\subseteq\R^2$
	and let
	$\mathcal V=\Span\mathcal X$. First note that if $\mathcal X\neq \Set{}$, then $\mathcal V$
	is non-empty because $\mathcal X\subseteq\mathcal V$ and if $\mathcal X=\Set{}$, then $\mathcal V=\Set{\vec 0}$,
	and so is still non-empty.
	
	Fix $\vec v,\vec u\in\mathcal V$. By definition there are $\vec x_1,\vec x_2,\ldots,\vec y_1,\vec y_2,\ldots\in\mathcal X$ 
	and scalars $\alpha_1,\alpha_2,\ldots,\beta_1,\beta_2,\ldots$ so that
	\[
		\vec v=\sum \alpha_i\vec x_i\qquad \vec u=\sum\beta_i\vec y_i.
	\]

	To verify property (i), observe that
	\[
		\vec u+\vec v=\sum\alpha_i\vec x_i + \sum\beta_i\vec y_i
	\]
	is also a linear combination of vectors in $\mathcal X$ (because all $\vec x_i$ and $\vec y_i$
	are in $\mathcal X$), and so $\vec u+\vec v\in	\Span\mathcal X=\mathcal V$.
	
	To verify property (ii), observe that for any scalar $\alpha$, 
	\[
		\alpha\vec v=\alpha\sum \alpha_i\vec x_i = \sum (\alpha\alpha_i)\vec x_i\in
		\Span\mathcal X=\mathcal V.
	\]
	Since $\mathcal V$ is non-empty and satisfies both properties (i) and (ii), it is a subspace.

	Now we will prove that every subspace is a span. Let $\mathcal V$ be a subspace
	and consider $\mathcal V'=\Span\mathcal V$.  Since taking a span may only enlarge a set, we know
	$\mathcal V\subseteq \mathcal V'$. If we establish that $\mathcal V'\subseteq\mathcal V$,
	then $\mathcal V=\mathcal V'=\Span\mathcal V$, which would complete the proof.

	Fix $\vec x\in\mathcal V'$. By definition, there are $\vec v_1,\vec v_2,\ldots,\vec v_n\in\mathcal V$ and scalars
	$\alpha_1,\alpha_2,\ldots,\alpha_n$ so that
	\[
		\vec x=\sum \alpha_i\vec v_i.
	\]
	Observe that 
	$\alpha_i\vec v_i\in\mathcal V$ for all $i$, since $\mathcal V$ is closed under scalar
	multiplication. It follows that $\alpha_1\vec v_1+\alpha_2\vec v_2\in\mathcal V$
	because $\mathcal V$ is closed under sums. Continuing, 
	$(\alpha_1\vec v_1+\alpha_2\vec v_2)+\alpha_3\vec v_3\in\mathcal V$ because
	$\mathcal V$ is closed under sums. By finite induction we see
	\[
		\vec x=\sum \alpha_i\vec v_i
		=\Big(\big((\alpha_1\vec v_1+\alpha_2\vec v_2)
		+\alpha_3\vec v_3\big)+\cdots+\alpha_{n-1}\vec v_{n-1} \Big)
		+\alpha_n\vec v_n\in\mathcal V.
	\]
	Thus $\mathcal V'\subseteq\mathcal V$, which completes the proof.
\end{proof}

The previous theorem is saying that spans and subspaces are two ways of talking about the same
thing. Spans provide a \emph{constructive} definition of lines/planes/volumes/etc. through the origin. That is,
when you describe a line/plane/etc. through the origin as a span, you're saying ``this is a line/plane/etc. through the origin
because every point in it is a linear combination of \emph{these specific vectors}''. In contrast, subspaces provide a \emph{categorical}
definition of lines/planes/etc. through the origin. 
When you describe a line/plane/etc. through the origin as a subspace, 
you're saying ``this is a line/plane/etc. through the origin because these \emph{properties} are satisfied'' even though
you might not be able to specify any of the vectors inside.


\begin{emphbox}[Takeaway]
	Spans and subspaces are two different ways of talking about the same objects: points/lines/planes/etc. through the origin.
\end{emphbox}

\Heading{Special Subspaces}
When thinking about $\R^n$ there are two special subspaces that are always available. The first is $\R^n$ itself.
$\R^n$ is obviously non-empty, and linear combinations of vectors in $\R^n$ remain in $\R^n$. The second is
the \emph{trivial subspace}, $\Set{\vec 0}$.

\SavedDefinitionRender{TrivialSubspace}

\begin{theorem}
	The trivial subspace is a subspace.
\end{theorem}
\begin{proof}
	First note that $\Set{\vec 0}$ is non-empty since $\vec 0\in\Set{\vec 0}$. Now, since
	$\vec 0$ is the only vector in $\Set{\vec 0}$, properties (i) and (ii) follow quickly:
	\[
		\vec 0+\vec 0=\vec 0\in \Set{\vec 0}
	\]
	and
	\[
		\alpha\vec 0=\vec 0\in\Set{\vec 0}.
	\]
\end{proof}

\Heading{Bases}

Let $\vec d=\mat{1\\2}$ and consider $\ell=\Span\Set{\vec d}$.

XXX Figure

We know that $\ell$ is a subspace and, for instance, $\ell=\Span\Set{\vec d,-2\vec d,\tfrac{1}{2}\vec d}$. However,
the simplest descriptions of $\ell$ involve the span of only one vector.


Analogously, let $\mathcal P=\Span\Set{\vec d_1,\vec d_2}$ be the plane
through the origin with direction vectors $\vec d_1$ and $\vec d_2$. There
are many ways to write $\mathcal P$ as a span, but the simplest ones
involve exactly two vectors. The idea of a \emph{basis} comes
from trying to find the simplest description of a subspace.

\SavedDefinitionRender{Basis}

In short, a basis for a subspace is a linearly independent set that spans that
subspace.

\begin{example}
	\label{EXLINEBASIS}
	Let $\ell=\Span\Set*{\mat{1\\2},\mat{-2\\-4}, \mat{1/2\\1}}$. Find
	two different bases for $\ell$.
	
	We are looking for a set of linearly independent vectors which span $\ell$.
	Notice that
    \[
		\Span\Set*{\mat{1\\2}} =
		\Span\Set*{\mat{-2\\-4}} =
		\Span\Set*{\mat{1/2\\1}} =
		\Span\Set*{\mat{1\\2},\mat{-2\\-4}, \mat{1/2\\1}} =
		\ell.
	\]
	Because $\Set*{\mat{1\\2}}$ is linearly independent and spans $\ell$,
	we have that $\Set*{\mat{1\\2}}$ is a basis for $\ell$.
	Similarly, $\Set*{\mat{1/2\\1}}$ is another basis for $\ell$.
\end{example}

Unpacking the definition of basis a bit more, we can see that for a 
subspace $\mathcal V$, a basis for $\mathcal V$ is a set of vectors
that is \emph{just the right size} to describe everything in $\mathcal V$.
It's not too big---because it is linearly independent, there are no
redundancies. It's not too small---because we require it to span $\mathcal V$\footnote{ 
If you're into British fairy tales, you might call a basis a \emph{Goldilocks set}.
}.

There are several facts everyone should know about bases:
\begin{enumerate}
	\item Bases are not unique. Every subspace (except the trivial subspace)
		has multiple bases.
	\item Given a basis for a subspace, every vector in the subspace can be written
		as a \emph{unique} linear combination of vectors in that subspace.
	\item Any two bases for the same subspace have the same number of elements.
\end{enumerate}

You can prove the first fact by observing that if $\mathcal B=\Set{\vec b_1,\vec b_2,\ldots}$ is a basis
with at least one element\footnote{ The empty set is a basis for the trivial subspace.}, then
$\Set{2\vec b_1,2\vec b_2,\ldots}$ is a different basis. The second fact is a consequence of all bases 
being linearly independent. The third fact is less obvious and takes some legwork to prove, so we will accept it
as is.

\Heading{Dimension}

Let $\mathcal V$ be a subspace. Though there are many bases for $\mathcal V$, they all
have the same number of vectors in them. And, this number says something fundamental about $\mathcal V$:
it tells us the maximum number of linearly independent vectors that can simultaneously exist in $\mathcal V$.
We call this number the \emph{dimension} of $\mathcal V$.

\SavedDefinitionRender{Dimension}

This definition agrees with our intuition about lines and planes: the dimension of a line through $\vec 0$ is $1$, and
the dimension of a plane through $\vec 0$ is $2$. It even tells us the dimension of the single point $\Set{\vec 0}$
is $0$\footnote{ The dimension of a line, plane, or point
not through the origin is defined to be the dimension of the subspace obtained
when translating it to the origin.}.

\begin{example}
	Find the dimension of $\R^2$.

	Since $\Set{\xhat, \yhat}$ is a basis for $\R^2$, we know $\R^2$ is
	two dimensional.
\end{example}

\begin{example}
	Let $\ell=\Span\Set*{\mat{1\\2},\mat{-2\\-4}, \mat{1/2\\1}}$.
	Find the dimension of the subspace $\ell$.

	This is the same subspace from the earlier example where we found
	$\Set*{\mat{1\\2}}$ and $\Set*{\mat{1/2\\1}}$
	were bases for $\ell$.
	The basis $\Set*{\mat{1\\2}}$ contains one element, and so
	$\ell$ is a one dimensional subspace\footnote{
	We could have considered $\Set*{\mat{1/2\\1}}$ or one of the many other bases for $\ell$
	and still reach the same conclusion: $\ell$ is one dimensional.}.
\end{example}

\begin{example}
	Let $A=\Set{(x_1,x_2,x_3,x_4)\given x_1+2x_2-x_3=0\text{ and }x_1+6x_4=0}$. Find a basis for and the dimension
	of $A$.

	XXX Finish
\end{example}

Like $\R^2$ and $\R^3$, whenever we discuss $\R^n$, we always have a standard basis that comes
along for the ride.

\SavedDefinitionRender{StandardBasisforRn}

The notation $\vec e_i$ is context specific. If we say $\vec e_i\in\R^2$,
then $\vec e_i$ must have exactly two components. If we say $\vec e_i\in\R^{45}$,
then $\vec e_i$ must have $45$ components. 
