\begin{exercises}
	\begin{problist}
		\prob  Indicate whether the following linear transformations are one-to-one and/or onto, as well as indicate whether they are invertible. Justify your answers.
		\begin{enumerate}
			\item   $\mathcal S:\R^2\to\R^2$, where $\mathcal S$ is a linear transformation that doubles every vector.
			\item   $\mathcal R:\R^2\to\R^2$, where $\mathcal R$ a linear transformation that rotates every vector clockwise by $72^\circ$.
			\item   $\mathcal P:\R^2\to\R^2$, where $\mathcal P$ a linear transformation that projects every vector onto the $y$-axis.
			\item   $\mathcal F:\R^2\to\R^2$, where $\mathcal F$ is a linear transformation that reflects every vector over the line $y=x$.
			\item   $T:\R^3\to\R^3$, where $T$ is a linear transformation induced by the matrix $M_T = \mat{1&2&3\\3&4&5\\5&6&7}$.
			\item   $U:\R^3\to\R^2$, where $U$ is a linear transformation induced by the matrix $M_U = \mat{1&2&3\\3&4&5}$.
		\end{enumerate}
		
		\prob Find the inverses, if possible, of the following matrices, or justify why it is not possible to find the inverses.
		    \begin{enumerate}
		        \item   $M_1 = \mat{2&3\\1&-1}$.
		        \item   $M_1 = \mat{1&0\\1&0}$.
		        \item   $M_3 = \mat{0&2&1\\1&0&1\\-2&3&0}$.
		        \item   $M_4 = \mat{0&-3&1&8\\1&0&-1&1\\2&-1&0&7}$.
		        \item   $M_5 = \mat{0&-3&1&2\\1&0&-1&1\\2&-1&0&0\\0&0&1&3}$.
		    \end{enumerate}
		
		\prob Solve the system $\systeme{2x+y=5,3x+7y=3}$ in two ways:
		    \begin{enumerate}
		        \item   using row reduction.
		        \item   using inverse matrices.
		    \end{enumerate}
		
		\prob Solve the system $\systeme{2x+2y+3z=4,2x+2y+z=0, 4x+5y+6z=2}$ in two ways:
		    \begin{enumerate}
		        \item   using row reduction.
		        \item   using inverse matrices.
		    \end{enumerate}
		    
		\prob 	Let $A=\mat{1&3&5\\0&2&0\\-1&0&2}$. 
		    \begin{enumerate}
		        \item Find $A^{-1}$ using elementary matrices.
		        \item Find the matrix $B$ which satisfies $BA=I$.
		        \item Decompose the matrix $B$ into elementary matrices. 
		    \end{enumerate}  
	
		\prob For each argument listed below, indicate whether it is correct or incorrect. Justify you answer.
            \begin{enumerate}
                \item   For an  arbitrary linear transformation $T:\R^m\to\R^n$, if $n \neq m$, then the linear transformation is not invertable. 
                \item   The matrix $M = \mat{1&0&0\\1&1&0}$ is an elementary matrix.
            \end{enumerate}
		
	\end{problist}
\end{exercises}
