\begin{exercises}
	\begin{problist}
		\prob For each transformation listed below, prove whether or not it is a linear transformation.
		\label{PROBSETMOD9-linnonlin}
		\begin{enumerate}
			\item $\mathcal A:\R^2\to\R^2$ defined by $\mathcal A\mat{x\\y}=\mat{-x\\y}$.
			\item $\mathcal B:\R^2\to\R^2$ defined by $\mathcal A\mat{x\\y}=\mat{-x-1\\y}$.
			\item $\Ident:\R^2\to\R^2$, the function that does nothing to its input.
			\item $\mathcal C:\R^2\to\R^2$, where $\mathcal C$ sends all vectors above the $x$-axis to $\vec 0$
				and all vectors on or below the $x$-axis to $-\yhat$.
		\end{enumerate}

		\prob Draw the image of the unit circle under each transformation listed in \ref{PROBSETMOD9-linnonlin}.

		\prob Let $M=\mat{1&-2&3\\-4&5&-6}$ and let $T_M$ be the corresponding matrix transformation.
		\begin{enumerate}
			\item Determine the domain and codomain of $T_M$.
			\item Calculate $T_M\left(\mat{2\\-1\\1}\right)$.
			\item Find the image of the standard basis vectors of the domain under $T_M$.
		\end{enumerate}

		\prob Find a matrix for each transformation below, or explain why no such matrix exists.
		\begin{enumerate}
			\item $\mathcal S:\R^{2}\to\R^{2}$, where $\mathcal S$ is the
				transformation that doubles every vector.

			\item $\mathcal R:\R^{2}\to\R^{2}$, where $\mathcal R$
				is rotation clockwise by $135^{\circ}$.

			\item $\mathcal T:\R^2\to\R^2$, where $\mathcal T$ translates every vector by $3\xhat$.

			\item $\mathcal P:\R^{2}\to\R^{2}$, where $\mathcal P$
				is projection onto the $y$-axis.

			\item $\mathcal F:\R^{2}\to\R^{2}$, where $\mathcal F$
				is reflection over the line
				$y=x$.
		\end{enumerate}

		\prob Let $S:\R^n\to\R^m$ and $T:\R^n\to\R^m$ be linear transformations,
		and define the transformation $R:\R^n\to\R^m$ by $R(\vec x)=S(\vec x)+T(\vec x)$.
		Show that $R$ is also linear.

		\prob For a fixed vector $\vec a\in\R^3$, define the function $D_{\vec a}$ by
		$D_{\vec a}(\vec x) = \vec a\cdot\vec x$.
		\begin{enumerate}
			\item Identify the domain and codomain of $D_{\vec a}$.
			\item Show that when $\vec a=\xhat$, then $D_{\vec a}$ is a linear transformation.
			\item Is $D_{\vec a}$ a linear transformation for all $\vec a$? Prove your claim.
			\item Find a matrix for $D_{\vec a}$ or explain why no such matrix exists.
		\end{enumerate}

		\prob Let $T:\R^2\to\R^2$ be a transformation with the property that $T(V)$ is a subspace
		whenever $V$ is a subspace. Is this enough information to conclude that $T$ is a linear
		transformation? Justify your answer.

		\prob For each statement below, determine whether it is true or false. Justify you answer.
		\begin{enumerate}
			\item Every transformation from $\R^n$ to $\R^m$ can be represented by a matrix.
			\item The image of a subspace under a linear transformation is not a subspace.
			\item A transformation that takes every vector in the domain to $\vec 0$ is not linear.
			\item Every matrix is a linear transformation.
			\item Parallel lines stay parallel under a linear transformation.
		\end{enumerate}

	\end{problist}
\end{exercises}
