\begin{exercises}
	\begin{problist}
		\prob For each transformation listed below, prove whether or not it is a
		linear transformation. \label{PROBSETMOD9-linnonlin}
		\begin{enumerate}
			\item $\mathcal{A}:\R^{2}\to\R^{2}$ defined by
				$\mathcal{A}\mat{x\\y}=\mat{-x\\y}$.

			\item $\mathcal{B}:\R^{2}\to\R^{2}$ defined by
				$\mathcal{B}\mat{x\\y}=\matc{-x-1\\y}$.

			\item $\Ident:\R^{2}\to\R^{2}$, the function that leaves its input unchanged.

			\item $\mathcal{C}:\R^{2}\to\R^{2}$, where $\mathcal{C}$ sends all vectors
				above the $x$-axis to $\vec 0$ and all vectors on or below the $x$-axis
				to $-\yhat$.
		\end{enumerate}
		\begin{solution}
			\begin{enumerate}
				\item Yes. $\mathcal{A}$ is a linear transformation. Let
					$\vec{u}= \mat{u_1\\u_2}$ and $\vec{v}= \mat{v_1 \\ v_2}$ be
					two vectors and $\alpha$ be a scalar. $\mathcal{A}(\vec{u}+
					\vec{v}) = \mathcal{A}\mat{u_1 + v_1 \\ u_2 + v_2}= \mat
					{-u_1 - v_1 \\ u_2 + v_2 }= \mat{-u_1 \\ u_2 }+ \mat
					{ - v_1 \\ v_2 }= \mathcal{A}\mat{u_1\\u_2}+ \mathcal{A}\mat
					{v_1 \\ v_2}= \mathcal{A}(\vec{u}) +\mathcal{A}(\vec{v})$ and
					$\mathcal{A}(\alpha \vec{u}) = \mathcal{A}\mat
					{\alpha u_1 \\ \alpha u_2}= \mat
					{ - \alpha u_1 \\ \alpha u_2}= \alpha \mat{ - u_1 \\u_2}=
					\alpha \mathcal{A}\mat{ u_1 \\u_2}= \alpha \mathcal{A}(\vec
					{u}) $ So $\mathcal{A}$ satisfies all the properties of a linear
					transformation.

				\item No. $\mathcal{B}\mat{0\\0}= \mat{-1\\0}\neq \mat{0\\0}$

				\item Yes. Let $\vec{u}= \mat{u_1\\u_2}$ and $\vec{v}= \mat
					{v_1 \\ v_2}$ be two vectors and $\alpha$ be a scalar.
					$\mathbf{id}(\vec{u}+\vec{v}) = \mathbf{id}\mat
					{u_1 + v_1 \\ u_2 + v_2}= \mat{u_1 + v_1 \\ u_2 + v_2 }=
					\mat{u_1 \\ u_2 }+ \mat{ v_1 \\ v_2 }= \mathbf{id}\mat
					{u_1\\u_2}+ \mathbf{id}\mat{v_1 \\ v_2}= \mathbf{id}(\vec{u}
					) +\mathbf{id}(\vec{v})$
					and
					$\mathbf{id}(\alpha \vec{u}) =\mathbf{id}\mat
					{\alpha u_1 \\ \alpha u_2}= \mat{ \alpha u_1 \\ \alpha u_2}=
					\alpha \mat{ u_1 \\u_2}= \alpha \; \mathbf{id}\mat
					{ u_1 \\u_2}= \alpha \; \mathbf{id}(\vec{u}) $
					So $\mathbf{id}$ satisfies all the properties of a linear
					transformation.

				\item No. As $\vec{0}$ is on the $x$-axis,
					$\mathcal{C}(\vec{0}) = - \vec{e}_{2}\neq \vec{0}$ .
			\end{enumerate}
		\end{solution}

		\prob Draw the image of the unit circle under each transformation listed
		in \ref{PROBSETMOD9-linnonlin}.
		\begin{solution}
			\begin{enumerate}
				\item Notice $\mathcal{A}$ is just reflection about $y$-axis. If
					you reflect all points on the circle about the $y$-axis you get
					back the unit circle.

				\item
					$\mathcal{B}\mat{x\\y}= \matc{-x-1\\y}= \mat{-x\\y}+ \mat
					{-1\\0}$. So the transformation $\mathcal{B}$ reflects over
					the $y$-axis and then translates. We already know the first
					operation keeps the circle as it is. So the final image is just
					a translated circle, that is unit circle with center at (-1,0).

				\item $\Ident$ leaves all points unchanged. So the image of the unit
					circle under $\Ident$ is still the unit circle.

				\item The unit circle under $\mathcal{C}$ is the set
					$\Set{(0,0), (0,-1)}$.
			\end{enumerate}
		\end{solution}

		\prob Let $M=\mat{1&-2&3\\-4&5&-6}$ and let $T_{M}$ be the corresponding
		matrix transformation.
		\begin{enumerate}
			\item Determine the domain and codomain of $T_{M}$.

			\item Calculate $T_{M}\left(\mat{2\\-1\\1}\right)$.

			\item Find the image of the standard basis vectors of the domain
				under $T_{M}$.
		\end{enumerate}
		\begin{solution}
			\begin{enumerate}
				\item Recall that an $m \times n$ matrix represents a
					transformation from $\R^{n}\rightarrow \R^{m}$. The given matrix
					$M$ is $2 \times 3$, so $T_{M}: \R^{3}\rightarrow \R^{2}$. Thus
					the domain of $T_{M}$ is $\R^{3}$ and codomain is $\R^{2}.$

				\item
					$T_{M}\left( \mat{2\\-1\\1}\right) = \mat
					{1 & -2 & 3 \\ -4 & 5 & -6}\mat{2\\-1\\1}= \mat{7\\ -19}$

				\item $T_{M}(\vec{e}_{1}) = \mat{1\\-4}$, $\;\;\; T_{M}(\vec{e}
					_{2}) = \mat{-2 \\ 5}$,
					$\;\;\; T_{M}(\vec{e}_{3}) = \mat{3\\-6}$
			\end{enumerate}
		\end{solution}

		\prob Find a matrix for each transformation below, or explain why no such
		matrix exists.
		\begin{enumerate}
			\item $\mathcal{S}:\R^{2}\to\R^{2}$, where $\mathcal{S}$ is the transformation
				that doubles every vector.

			\item $\mathcal{R}:\R^{2}\to\R^{2}$, where $\mathcal{R}$ is rotation
				clockwise by $135^{\circ}$.

			\item $\mathcal{T}:\R^{2}\to\R^{2}$, where $\mathcal{T}$ translates every
				vector by $3\xhat$.

			\item $\mathcal{P}:\R^{2}\to\R^{2}$, where $\mathcal{P}$ is projection
				onto the $y$-axis.

			\item $\mathcal{F}:\R^{2}\to\R^{2}$, where $\mathcal{F}$ is reflection
				over the line $y=x$.
		\end{enumerate}
		\begin{solution}
			\begin{enumerate}
				\item \label{itm:first} $\mat{2 & 0 \\ 0& 2}$

				\item To determine the image of $\vec{e}_{1}, \vec{e}_{2}$, we use
					trigonometry. Note
					$\mathcal{R}\mat{1\\0}= \mat
					{- \cos (45^{o}) \\ - \sin (45^{o})}= \mat
					{- 1/ \sqrt{2} \\ - 1/ \sqrt{2}}$
					and
					$\mathcal{R}\mat{0\\1}= \mat
					{ \cos (45^{o}) \\ - \sin (45^{o})}= \mat
					{ 1/ \sqrt{2} \\ -1/ \sqrt{2}}$. To see this draw pictures,
					draw angles and remember that $\vec{e}_{1}$ and
					$\vec{e}_{2}$ are unit vectors. Thus the matrix of $\mathcal{R}$
					is $\mat
					{- \frac{1 }{\sqrt{2}} & \frac{1 }{\sqrt{2}}\\ - \frac{1}{\sqrt{2}} & -\frac{1}{\sqrt{2}}}$.

				\item No such matrix exists as this is not a linear
					transformation.

				\item \label{itm:fourth} $\mat{0 & 0 \\ 0 & 1}$

				\item \label{itm:fifth} $\mat{0 & 1 \\ 1 & 0}$
			\end{enumerate}
		\end{solution}

		\prob Let $S:\R^{n}\to\R^{m}$ and $T:\R^{n}\to\R^{m}$ be linear
		transformations, and define the transformation $R:\R^{n}\to\R^{m}$ by $R
		(\vec x)=S(\vec x)+T(\vec x)$. Show that $R$ is also linear.
		\begin{solution}
			Let $\vec{u}$ and $\vec{v}$ be two vectors in $\R^{n}$ and $c$ be a
			scalar. Then we have,
			$R(\vec{u}+ \vec{v}) = S(\vec{u}+ \vec{v}) + T(\vec{u}+ \vec{v})$. Since
			given that both $S, T$ are linear transformations, we get
			$S(\vec{u}+ \vec{v}) + T(\vec{u}+ \vec{v}) = S(\vec{u})+ S(\vec{v})
			+ T(\vec{u})+T (\vec{v}) = (S(\vec{u})+ T(\vec{u})) + (S(\vec{v})+ T
			(\vec{v})) = R(\vec{u})+ R(\vec{v})$. Hence we have,
			$R(\vec{u}+ \vec{v})=R(\vec{u})+ R(\vec{v})$. Similarly,
			$R(c \vec{u})= S(c \vec{u})+T(c \vec{u}) = cS( \vec{u})+cT( \vec{u})
			= cR( \vec{u})$. Thus $R$ is also linear.
		\end{solution}

		\prob For a fixed vector $\vec a\in\R^{3}$, define the function
		$D_{\vec a}$ by $D_{\vec a}(\vec x) = \vec a\cdot\vec x$.
		\begin{enumerate}
			\item Identify the domain and codomain of $D_{\vec a}$.

			\item Show that when $\vec a=\xhat$, then $D_{\vec a}$ is a linear transformation.

			\item Is $D_{\vec a}$ a linear transformation for all $\vec a$? Prove
				your claim.

			\item Find a matrix for $D_{\vec a}$ or explain why no such matrix
				exists.
		\end{enumerate}
		\begin{solution}
			\begin{enumerate}
				\item Since dot product is only defined for vectors in the same
					space, if $\vec{a}\in \R^{3}$, $\vec{x}$ must also be in
					$\R^{3}$. So the domain of $D_{\vec{a}}$ is $\R^{3}.$

				\item Let $\vec{u}= \mat{u_1\\u_2\\u_3}$ and
					$\vec{v}= \mat{v_1 \\ v_2\\v_3}$ be two vectors and $\alpha$
					be a scalar. Then
					\begin{align*}
						D_{\vec{e}_1}(\vec{u}+ \vec{v}) & = \mat{1\\0\\0}\cdot \mat{u_1 + v_1 \\ u_2 + v_2 \\ u_3+v_3}= u_{1}+ v_{1}           \\
						                                & = \mat{1\\0\\0}\cdot \mat{u_1 \\ u_2\\u_3}+ \mat{1\\0\\0}\cdot \mat{v_1 \\ v_2\\v_3} \\
						                                & = D_{\vec{e}_1}(\vec{u}) + D_{\vec{e}_1}(\vec{v})
					\end{align*} and
					\begin{align*}
						D_{\vec{e}_1}(\alpha \vec{u}) & = \mat{1\\0\\0}\cdot \mat{\alpha u_1 \\ \alpha u_2\\ \alpha u_3}= \alpha u_{1} \\
						                              & = \alpha \left( \mat{1\\0\\0}\cdot \mat{u_1 \\ u_2\\u_3}\right )               \\
						                              & = \alpha D_{\vec{e}_1}(\vec{u})
					\end{align*}

				\item Yes, $D_{\vec{a}}$ is a linear transformation for all vectors
					$\vec{a}$. The properties of linear transformation can be
					proved from properties of dot product. Let $\vec{u}$ and $\vec
					{v}$ be two vectors and $\alpha$ be a scalar. Then
					$D_{\vec{a}}(\vec{u}+ \vec{v})= \vec{a}\cdot (\vec{u}+ \vec
					{v}) = \vec{a}\cdot \vec{u}+ \vec{a}\cdot \vec{v}= D
					_{\vec{a}}(\vec{u}) + D_{\vec{a}}(\vec{v})$
					and
					\[
						 D_{\vec{a}}(\alpha \vec{u}) = \vec{a}\cdot ( \alpha \vec
						{u}) = \alpha \; \vec{a}\cdot \vec{u}= \alpha D_{\vec{a}}
						(\vec{u})
					\]

				\item $D_{\vec{a}}: \R^{3}\rightarrow \R$. Thus the matrix, say
					$M_{D}$, will be $1 \times 3$. If
					$\vec{a}= \mat{a_1\\a_2\\ a_3}$ Then, $M_{D}= \mat
					{a_1 & a_2 & a_3}$
			\end{enumerate}
		\end{solution}

		\prob Let $T:\R^{2}\to\R^{2}$ be a transformation with the property that
		$T(V)$ is a subspace whenever $V$ is a subspace. Is this enough
		information to conclude that $T$ is a linear transformation? Justify your
		answer.
		\begin{solution}
			No. Here is a (counter) example of a transformation which is not linear
			: $T : \R^{2}\rightarrow \R^{2}$ is such that $T$ keeps the coordinates
			of the points on $x$-axis unchanged and sends every other point to $\vec
			{0}$. That is, $T$ is given by $T \mat{x\\y}= \mat{0\\0}$ if $y\neq
			0$, and $T\mat{x\\0}= \mat{x\\0}$.

			Then $T$ satisfies the given condition : $T(\R^{2})$ is the $x$-axis
			which is a subspace.
			$T(\vec{0})= \vec{0}\Rightarrow \{T(\vec{0}) \} = \{\vec{0}\}$, so $T$
			sends the zero subspace to the zero subspace. Other subspaces of
			$\R^{2}$ are lines through the origin. $T$ sends all such lines except
			for the $x$-axis to the subspace $\{ \vec{0}\}$. $T$ sends the
			subspace $x$-axis to $x$-axis. Thus $T(V)$ is a subspace whenever $V$
			is a subspace. But clearly $T$ is not linear. Take for example : $T
			\mat{1\\1}= \mat{0\\0}$ by construction. But
			$\mat{1\\1}= \mat{1\\0}+ \mat{0\\1}$ and
			$\left( T\mat{1\\0}+ T \mat{0\\1}\right)= \mat{1\\0}+ \mat{0\\0}=
			\mat{1\\0}\neq T \mat{1\\1}$
		\end{solution}

		\prob For each statement below, determine whether it is true or false.
		Justify your answer.
		\begin{enumerate}
			\item Every transformation from $\R^{n}$ to $\R^{m}$ can be
				represented by a matrix.

			\item The image of a subspace under a linear transformation is not a
				subspace.

			\item A transformation that takes every vector in the domain to
				$\vec 0$ is not linear.

			\item Every matrix is a linear transformation.

			\item Parallel lines stay parallel under a linear transformation.
		\end{enumerate}
		\begin{solution}
			\begin{enumerate}
				\item False. Take $T : \R^{2}\rightarrow \R^{2}$ given by $T
					\mat{x\\y}= \mat{x-1\\0}$. If there were a matrix
					$\mat{a & b \\ c& d}$ representing this transformation, then
					consider $T\mat{1\\0}$ and $T\mat{2\\0}$.
					$T\mat{1\\0}=\mat{a & b \\ c& d}\mat{1\\0}=\mat{0\\0}$ which
					implies that $a=0, c=0$. But $T\mat{2\\0}=\mat
					{a & b \\ c& d}\mat{2\\0}= \mat{1\\0}$ which implies $a=
					\tfrac{1}{2},c=0$ --- a contradiction! So no such matrix
					exists. The correct statement is the following: Every
					``linear" transformation from $\mathbb{R}^{n}$ to
					$\mathbb{R}^{m}$ can be represented by a matrix.

				\item False. This follows directly from the theorem given in this
					chapter that if $T : \mathbb{R}^{n}\rightarrow \mathbb{R}
					^{m}$ is a linear transformation, then $T$ takes subspaces
					to subspaces.

				\item False. The transformation is linear. Check the properties.
					Note: this transformation is sometimes called ``the zero
					transformation.'

				\item False. A matrix is just a box of numbers, it has no
					meaning unless we give it meaning. We can specify a linear transformation
					by using a matrix, but a matrix by itself is not a linear
					transformation.

				\item False. There is a theorem in this module which explains this
					point. Suppose $T:\mathbb{R}^{2}\rightarrow \mathbb{R}^{2}$
					is the tranformation which takes all vectors to the zero
					vector, $\ell_{1}$ is given by the equation $y=x+1$ and $\ell
					_{2}$ is given by the equation $y=x+2$. Then $T$ is a linear
					transformation but $T(\ell_{1})=T(\ell_{2})=\Set{(0,0)}$. Hence
					it doesn't make sense to say $\ell_{1}$ and $\ell_{2}$ are parallel
					under $T$.
			\end{enumerate}
		\end{solution}
		\prob Let $\mathcal T:\R^2\to\R^2$ be the transformation that doubles the length
		of its input. The following statements about $\mathcal T$ are either incorrect or incomplete.
		Fix each statement so that it is correct and complete.
		\begin{enumerate}
			\item $\mathcal T=\mat{2&0\\0&2}$.
			\item Since $\mathcal T\vec x=2\vec x$ for every $\vec x$, we can
				say $\mathcal T=2$.
			\item $\mathcal T$ is a linear transformation because $2(\vec x+\vec y)=2\vec x+2\vec y$.
		\end{enumerate}
		\begin{solution}
			\begin{enumerate}
				\item $\mathcal T$ can be defined by $\mathcal T\vec x=\mat{2&0\\0&2}\vec x$.
				\item Since $\mathcal T\vec x=2\vec x$ for every $\vec x\in\R^2$ we can
					define $\mathcal T$ as the function which multiplies its input by the scalar two.
				\item $\mathcal T$ is a linear transformation because $\mathcal T(\vec x+\vec y)=2(\vec x+\vec y)=2\vec x+2\vec y=
					\mathcal T\vec x+\mathcal T\vec y$
					and $\mathcal T(\alpha\vec x)=2\alpha\vec x=\alpha2\vec x=\alpha\mathcal T\vec x$
					for all $\vec x,\vec y\in \R^2$ and all scalars $\alpha$.

			\end{enumerate}
		\end{solution}
	\end{problist}
\end{exercises}
